Holomorphic field theories and higher algebra

### 2024-09-16 draft.tex
chugging

In this section we describe several examples of holomorphic field theories,
close to the style we used for holomorphic Chern-Simons theory.

@@

We turn to a formal definition underpinning the formal moduli spaces of the holomorphic field theories that we will be considering.

\begin{dfn} 
A {\em holomorphic dg Lie algebra} on a complex manifold $X$ is
\begin{itemize}
\item a graded holomorphic vector bundle $V$ on $X$ whose sheaf of holomorphic functions is $\cV^{hol}$, and
\item a holomorphic differential operator $Q^{hol} \colon \cV^{hol} \to \cV^{hol}$ of cohomological degree one and a holomorphic bidifferential operator $[\cdot,\cdot] \colon \cV^{hol} \times \cV^{hol} \to \cV^{hol}$. 
\end{itemize}
This data is required to endow $(\cV^{hol}, Q^{hol}, [\cdot,\cdot])$ with the structure of a dg Lie algebra.
\end{dfn}

>>>>

In this section we describe several examples of holomorphic field theories,
in the style we used for holomorphic Chern-Simons theory.
Our aim here is to give a sense of how take physical ideas and find holomorphic analogs.

@@

We now turn to giving a mathematical definition that incorporates insights from derived geometry.
We will stick with studying perturbative field theory: 
we fix a solution $\phi_0$ to the equations of motion and study formal deformations of it.
In other words, we want to study the formal derived geometry of the moduli of solutions to the equations of motion.

Here we can exploit the heuristic principle that every derived deformation problem (in characteristic zero) is described by a dg Lie algebra.\footnote{Or, sometimes more conveniently, by an $L_\infty$ algebra.}
That is, if $\cM$ is a derived stack and $p: \Spec(\CC) \to \cM$ is a point, 
then the formal neighborhood $\cM^\wedge_p$ of $p$ is modeled by the Maurer-Cartan locus of some dg Lie algebra $\fg_p$.\footnote{More technically, the shifted tangent complex $\TT_p \cM[-1]$ comes equipped with a homotopy-coherent Lie algebra structure, 
and this determines a functor from small (i.e., artinian local) nonnegatively-graded dg algebras to the $\infty$-category of spaces.}
This idea goes back, at least, to Deligne, Drinfeld, and Schlessinger-Stasheff, 
but Hinich, Lurie, and Pridham have given a precise articulation of the {\em fundamental theorem of derived deformation theory}:
there is an equivalence of $\infty$-categories between formal moduli spaces and dg Lie algebras.

Applying this perspective to classical field theory was prominently and successfully advocated by Kontsevich, 
and it is an essential component of the formalism developed by Costello.
We mimic this approach here.

\begin{dfn} 
A {\em holomorphic local Lie algebra} on a complex manifold $X$ is
\begin{itemize}
\item a graded holomorphic vector bundle $V$ on $X$ whose sheaf of holomorphic functions is $\cV^{hol}$, and
\item a holomorphic differential operator $Q^{hol} \colon \cV^{hol} \to \cV^{hol}$ of cohomological degree one and a holomorphic bidifferential operator $[\cdot,\cdot] \colon \cV^{hol} \times \cV^{hol} \to \cV^{hol}$. 
\end{itemize}
This data is required to endow $(\cV^{hol}, Q^{hol}, [\cdot,\cdot])$ with the structure of a sheaf of dg Lie algebras.
\end{dfn}

We view such a sheaf $\cL$ of dg Lie algebras as describing a sheaf of formal moduli spaces.
To each open $U$, we study the formal moduli space associated to $\cL(U)$ and interpret it as ``deformations of a solution $\phi_0|_U$ to the equations of motion on~$U$.''

We now rephrase this data in the style of complex differential geometry and then further into more physical terminology.
\owen{Keep going!}
